### 2024-03-22 doc/sections/mav-syntax.tex
Add DSL for BV connectives

\begin{code}[hide]
  module mav-syntax (Atom : Set) where
\end{code}
\section{Multiplicative-Additive System Virtual}\label{sec:mav-syntax}

@@

Formulas:
\begin{code}[hide]
  infix 20 _⁺
  infix 20 _⁻
  infix 10 _⅋_
  infix 10 _⊗_
  infix 10 _&_
  infix 10 _⊕_
  infix 10 _▷_
\end{code}

\begin{code}
  data Formula : Set where
    I    : Formula
    _⁺   : Atom → Formula
    _⁻   : Atom → Formula
    _⅋_  : Formula → Formula → Formula
    _⊗_  : Formula → Formula → Formula
    _&_  : Formula → Formula → Formula
    _⊕_  : Formula → Formula → Formula
    _▷_  : Formula → Formula → Formula
\end{code}

\begin{displaymath}
  P, Q
  \Coloneq A^{+}
  \mid     A^{-}
  \mid     I
  \mid     P \bvtens Q
  \mid     P \bvparr Q
  \mid     P \bvwith Q
  \mid     P \bvplus Q
  \mid     P \bvseq  Q
\end{displaymath}

\begin{code}[hide]
  variable
    A A′ A₁ A₂ : Atom
    P P′ P₁ P₂ : Formula
    Q Q′ Q₁ Q₂ : Formula
    R R′ R₁ R₂ : Formula
    S S′ S₁ S₂ : Formula
\end{code}

Negation:
% \begin{displaymath}
%   \begin{array}{lcl}
%     (a)^\perp           & = & a^\perp                     \\
%     (a^\perp)^\perp     & = & a                           \\
%     (I)^\perp           & = & I                           \\
%     (P \otimes Q)^\perp & = & (P)^\perp \parr   (Q)^\perp \\
%     (P \parr   Q)^\perp & = & (P)^\perp \otimes (Q)^\perp \\
%     (P \with   Q)^\perp & = & (P)^\perp \oplus  (Q)^\perp \\
%     (P \oplus  Q)^\perp & = & (P)^\perp \with   (Q)^\perp \\
%     (P ; Q)^\perp       & = & (P)^\perp ; (Q)^\perp
%   \end{array}
% \end{displaymath}

\begin{code}[hide]
  infix 15 ¬_
\end{code}

\begin{code}
  ¬_ : Formula → Formula
  ¬ I          = I
  ¬ A ⁺        = A ⁻
  ¬ A ⁻        = A ⁺
  ¬ (P  ⅋  Q)  = ¬ P  ⊗  ¬ Q
  ¬ (P  ⊗  Q)  = ¬ P  ⅋  ¬ Q
  ¬ (P  &  Q)  = ¬ P  ⊕  ¬ Q
  ¬ (P  ⊕  Q)  = ¬ P  &  ¬ Q
  ¬ (P  ▷  Q)  = ¬ P  ▷  ¬ Q
\end{code}

>>>>

\section{Multiplicative-Additive System Virtual}\label{sec:mav-syntax}

@@

Formulas:
\begin{displaymath}
  P, Q
  \Coloneq A^{+}
  \mid     A^{-}
  \mid     \Unit
  \mid     P \Tens Q
  \mid     P \Parr Q
  \mid     P \With Q
  \mid     P \Plus Q
  \mid     P \Seq  Q
\end{displaymath}

Negation:
\begin{displaymath}
  \begin{array}{lcl}
    \Dual(\Pos(A))   & = & \Neg(A)                 \\
    \Dual(\Neg(A))   & = & \Pos(A)                 \\
    \Dual(\Unit)     & = & \Unit                   \\
    \Dual(P \Tens Q) & = & \Dual(P) \Parr \Dual(Q) \\
    \Dual(P \Parr Q) & = & \Dual(P) \Tens \Dual(Q) \\
    \Dual(P \With Q) & = & \Dual(P) \Plus \Dual(Q) \\
    \Dual(P \Plus Q) & = & \Dual(P) \With \Dual(Q) \\
    \Dual(P \Seq  Q) & = & \Dual(P) \Seq  \Dual(Q)
  \end{array}
\end{displaymath}
